Formal Construction of Microcontroller Instruction Set Model Using B

### 2011-10-07 papers/ArticleZ80/source/paper.tex
Teste de commit

\begin{abstract}
  This paper describes an approach to model the functional aspects of
  the instruction set of microcontroller platforms and an embedded software
  verified up to assembly level. These models were developed using the notation
  of the B method. The paper presents specifically the case of the Z80 
  platform and case study software that can be used in tanks of the petroleum
  industry. This work is a contribution towards the extension of the B method
  to handle developments up to the assembly level code.
\end{abstract}
%
%\keywords{ Validation, Verification, Microcontroller, Hardware}
\paragraph[Keywords]{ \textbf{Keywords}: Validation, Verification,  Embedded Software and
Hardware}

>>>>

\begin{abstract}

  This paper describes an approach to model the functional aspects of
  the instruction set of microcontroller platforms and an embedded software
  verified up to assembly level. These models were developed using the notation
  of the B method. The paper presents specifically the case of the Z80 
  platform and case study software that can be used in tanks of the petroleum
  industry. This work is a contribution towards the extension of the B method
  to handle developments up to the assembly level code.
\end{abstract}
%
%\keywords{ Validation, Verification, Microcontroller, Hardware}
%
\paragraph[Keywords]{ \textbf{Keywords}: Validation, Verification,  Embedded Software and
Hardware}
